### 2020-05-28 serial.tex
bibtweak

Our study underlines the importance of carefully defining measured epidemiological time distributions.
Previous studies have shown that it matters whether generation
intervals are measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
we generalize these ideas and show that they apply to other epidemiological distributions.
Changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series of symptomatic cases or infected cases from the reports of confirmed cases by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential, shim2020transmission});
these studies effectively assume constant backward delay distributions.
Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using dynamical approaches that model incidence as well as reporting delays explicitly (e.g., \cite{flaxman2020estimating}).

>>>>

Our study underlines the importance of carefully defining measured epidemiological time distributions.
Previous studies have shown that it matters whether generation
intervals are measured forward or backward \citep{nishiura2010time,champredon2015intrinsic,britton2019estimation};
we generalize these ideas and show that they apply to other epidemiological distributions.
Changes in the backward delay distributions due to changing cohort sizes are expected to be a pervasive feature of outbreak dynamics.
Recent analyses of COVID-19 epidemics have attempted to reconstruct epidemic time series of symptomatic cases or infected cases from the reports of confirmed cases by using time-independent delay distributions from infection or symptom onset to reporting (e.g., \cite{tempvar, park2020potential,scire2020reproductive,shim2020transmission});
these studies effectively assume constant backward delay distributions.
Although such approaches may be able to roughly match the time scale of an epidemic, we recommend using dynamical approaches that model incidence as well as reporting delays explicitly (e.g., \cite{flaxman2020estimating}).
